---
title: "Test Run"
output: html_document
---

> Bedtools need to be installed and added to your PATH. We suggest using v2.17.0, which has been provided in the external_tools folder for you to install. Other versions might be incompatible because of modification of input arguments for some of the sub-functions of bedtools.

Recalibrate mutation rate with divergence score for manuscript data.

```{r}
library(data.table)
library(parallel)
source("../lib/TADA_Annotation.R")
```

### Adjust mutation rate 

```{r}
TADA_A_adjust_mutation_rate(mut_file = "./test_simulated_DNM.bed ",
                            window_file = "./test_windows.txt",
                            sample_size = 5000, 
                            scale_features = c("GC_content", "div_score"),
                            scaling_file_name = "test_simulated_windows_mutrate_with_div_score_scaling_file_for_test_DNM.txt")
```

### Read in DNM data, annotation data and mutation rate data
```{r}
compact_data <- TADA_A_read_info(mut_files = c("test_simulated_DNM_with_allele_info.txt"),
                                 window_file = "test_windows.txt",
                                 mutrate_scaling_files = c("test_simulated_windows_mutrate_with_div_score_scaling_file_for_test_DNM.txt"),
                                 sample_sizes = c(5000),
                                 gene_prior_file = "test_gene_prior.txt",
                                 nonAS_noncoding_annotations = c("test_non_allele_specific_annotation_1.bed"),
                                 AS_noncoding_annotations = NA,
                                 report_proportion = 2000/18665,
                                 chunk_partition_num =1,
                                 node_n = 1,
                                 mutrate_ref_files = c("test_windows_extended_1bp_for_getting_base_level_mutrate.bed.fasta.tri.alt_A.mutrate.bw", "test_windows_extended_1bp_for_getting_base_level_mutrate.bed.fasta.tri.alt_C.mutrate.bw", "test_windows_extended_1bp_for_getting_base_level_mutrate.bed.fasta.tri.alt_G.mutrate.bw", "test_windows_extended_1bp_for_getting_base_level_mutrate.bed.fasta.tri.alt_T.mutrate.bw")
)

```

### Estimate relative risks
```{r}
TADA_A_RR_estimate(data = compact_data$base_info, selected_annotations = c(1), gene_prior_file = "test_gene_prior.txt", optimization_iteration = 2000)
```
